MS_CNuptake.Rmd

### 2022-07-12 MS_CNuptake.Rmd
figures outputted

# Setup 
```{r setup, include=FALSE}
rm(list=ls())
library(MLmetrics)
library(vhs)
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
#remotes::install_github("cj-holmes/vhs")
devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/")
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

### BP grassland
```{r}
#check tnpp grassland
#not filtering any management/non-management! while previous do so
#removing tiandi's grassland
NPP_grassland <- subset(NPP_all,pft=="Grassland" & is.na(Nmin)==TRUE)
grassland_sitemean <- aggregate(NPP_grassland,by=list(NPP_grassland$site), FUN=mean, na.rm=TRUE)

@@

b1 <- as.ggplot(~barplot(vif_bp, main = "VIF of Forest BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b2 <- as.ggplot(~barplot(vif_anpp_tnpp, main = "VIF of Forest ANPP/BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b3 <- as.ggplot(~barplot(vif_anpp_leafnpp, main = "VIF of Forest leaf-NPP/ANPP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b4 <- as.ggplot(~barplot(vif_bp_grass, main = "VIF of Grassland BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "ln PPFD", "ln vpd", "ln soil C/N", "fAPAR")))
#plot_grid(b1,b2,b3,b4,
#          labels = c('(a)','(b)','(c)','(d)'),
#          ncol=2,label_x = 0.9,label_y=0.92)+white
#ggsave(paste("~/data/output/newphy_vif_figs.jpg",sep=""),width = 10, height = 13)
```

@@

```{r}
#fig.2 validation
#plot_grid(p1,p2,p5,
#          p8,p9,p10,
#          p3,p4,p11,
#          p6,p12,p7, 
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
#          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
#ggsave(paste("~/data/output/newphy_fig2.jpg",sep=""),width = 24, height = 25)

@@

#plot_grid(a3,a4,a5,a6,a7,a8,
#          a9,a10,a11,a12,a13,a14,
#          nrow=2,
#          rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' '))

#this is for showing points
#ggsave(paste("~/data/output/newphy_fig3_SI.jpg",sep=""),width = 20, height = 10*(2/3))
```

@@

#plot_grid(a3,a4,a5,a6,a7,a8,
#          a9,a10,a11,a12,a13,a14,
#          nrow=2,
#          rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' '))
#ggsave(paste("~/data/output/newphy_fig3.jpg",sep=""),width = 20, height = 10*(2/3))
```

@@

#plot_grid(a1,a2,a3,a4,a5,a6,a7,a8,a9,
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
#ggsave(paste("~/data/output/newphy_fig4.jpg",sep=""),width = 22, height = 10)

#plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
#ggsave(paste("~/data/output/newphy_fig4_parallel.jpg",sep=""),width = 22, height = 10)
```

### global maps for effect of each factor NUE (not used now)
```{r}
gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_CNrt")]),varnam = "nue_CNrt",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15);g2 <- gg$gglegend

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_age")]),varnam = "nue_age",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4","royalblue3","wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g3 <- gg$ggmap +labs(title = "Age")+theme_grey(base_size = 15);g4 <- gg$gglegend+labs(title = ~paste("years"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_fAPAR")]),varnam = "nue_fAPAR",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4","royalblue3", "wheat","tomato3"),
                breaks = seq(-0.04,0.04,0.01))
g5 <- gg$ggmap +labs(title = "fAPAR")+theme_grey(base_size = 15);g6 <- gg$gglegend

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_PPFD")]),varnam = "nue_PPFD",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3","tomato4"),
                breaks = seq(-0.08,0.12,0.02))
g7 <- gg$ggmap +labs(title = "PPFD")+theme_grey(base_size = 15);g8 <- gg$gglegend + labs(title =~paste(mu, "mol m"^-2,"s"^-1))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_Tg")]),varnam = "nue_Tg",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.30,0.30,0.10))
g9 <- gg$ggmap +labs(title =~paste(T[g]))+theme_grey(base_size = 15);g10 <- gg$gglegend + labs(title =~paste("\u00B0C"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_vpd")]),varnam = "nue_vpd",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.20,0.30,0.05))
g11 <- gg$ggmap +labs(title = "D")+theme_grey(base_size = 15);g12 <- gg$gglegend+ labs(title =~paste("kPa"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_vcmax25")]), varnam = "nue_vcmax25",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.2,0.2,0.04))
g15 <- gg$ggmap +labs(title =~paste(V[cmax25]))+theme_grey(base_size = 15);g16 <- gg$gglegend+ labs(title =~paste(mu, "mol m"^-2,"s"^-1))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_LMA")]),varnam = "nue_LMA",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g17 <- gg$ggmap +labs(title = "LMA")+theme_grey(base_size = 15);g18 <- gg$gglegend+ labs(title =~paste("g ","m"^-2))

#plot_grid(g1,g2,g3,g4,g5,g6,
#          g7,g8,g9,g10,g11,g12,
#          g15,g16,g17,g18,
#          nrow=3,rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' ',
#                     '(g)',' ','(h)',' '),label_size = 15)+white
#
#ggsave(paste("~/data/output/newphy_fig4_not_used.jpg",sep=""),width = 20, height = 10)

g1
g2
g3
g4
g5
g6
g7
g8
g9
g10
g11
g12
g15
g16
g17
g18
```

@@

#plot_grid(d1,d2,d3,d4,d5,d6,
#          d7,d8,d9,d10,d11,d12,
#          d13,d14,d15,d16,
#          nrow=3,rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' ',
#                     '(g)',' ','(h)',' '),label_size = 15)+ white

#ggsave(paste("~/data/output/newphy_figS2.jpg",sep=""),width = 20, height = 10)
d1
d2
d3
d4
d5
d6
d7
d8
d9
d10
d11
d12
d13
d14
d15
d16
```

@@

## TRENDY analysis- BP
```{r}

@@

Fit models with environmental factors
```{r}

@@

#not fitting model basing on stepwise, just directly include all
d1 <- na.omit(NPP_statistical[,c("lon","lat","CABLE_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d1<- aggregate(d1,by=list(d1$lon,d1$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t1 <- stepwise_lm(d1,"CABLE_NPP")
t1[[2]]
#mod1 <- (lm(CABLE_NPP~fAPAR_a+Tg_a+vpd_a,data=d1))
mod1 <- (lm(CABLE_NPP~Tg_a+PPFD_a+vpd_a,data=d1))
summary(mod1)

d2 <- na.omit(NPP_statistical[,c("lon","lat","ISAM_npp","Tg_a","PPFD_a","vpd_a","site_a")])
d2<- aggregate(d2,by=list(d2$lon,d2$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t2 <- stepwise_lm(d2,"ISAM_npp")
t2[[1]]
t2[[2]]
mod2 <- (lm(ISAM_npp~Tg_a+PPFD_a+vpd_a,data=d2))
summary(mod2)

d3 <- na.omit(NPP_statistical[,c("lon","lat","ISBA_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d3<- aggregate(d3,by=list(d3$lon,d3$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t3 <- stepwise_lm(d3,"ISBA_NPP")
t3[[2]]
mod3 <- (lm(ISBA_NPP~Tg_a+PPFD_a+vpd_a,data=d3))
summary(mod3)

d4 <- na.omit(NPP_statistical[,c("lon","lat","JULES_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d4<- aggregate(d4,by=list(d4$lon,d4$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t4 <- stepwise_lm(d4,"JULES_NPP")
t4[[2]]
mod4 <- (lm(JULES_NPP~Tg_a+PPFD_a+vpd_a,data=d4))
summary(mod4)

d5 <- na.omit(NPP_statistical[,c("lon","lat","LPJ_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d5<- aggregate(d5,by=list(d5$lon,d5$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t5 <- stepwise_lm(d5,"LPJ_NPP")
t5[[2]]
mod5<- (lm(LPJ_NPP~Tg_a+PPFD_a+vpd_a,data=d5))
summary(mod5)

d6 <- na.omit(NPP_statistical[,c("lon","lat","ORCHIDEE_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d6<- aggregate(d6,by=list(d6$lon,d6$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t6 <- stepwise_lm(d6,"ORCHIDEE_NPP")
t6[[2]]
mod6<- (lm(ORCHIDEE_NPP~Tg_a+PPFD_a+vpd_a,data=d6))
summary(mod6)

d7 <- na.omit(NPP_statistical[,c("lon","lat","ORCHICNP_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d7<- aggregate(d7,by=list(d7$lon,d7$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t7 <- stepwise_lm(d7,"ORCHICNP_NPP")
t7[[2]]
mod7 <- (lm(ORCHICNP_NPP~Tg_a+PPFD_a+vpd_a,data=d7))
summary(mod7)

d8 <- na.omit(NPP_statistical[,c("lon","lat","SDGVM_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d8<- aggregate(d8,by=list(d8$lon,d8$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t8 <- stepwise_lm(d8,"SDGVM_NPP")
t8[[2]]
mod8<- (lm(SDGVM_NPP~Tg_a+PPFD_a+vpd_a,data=d8))
summary(mod8)

d9 <- na.omit(NPP_statistical[,c("lon","lat","CLASS_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d9<- aggregate(d9,by=list(d9$lon,d9$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t9 <- stepwise_lm(d9,"CLASS_NPP")
t9[[2]]
mod9<- (lm(CLASS_NPP~Tg_a+PPFD_a+vpd_a,data=d9))
summary(mod9)

d10 <- na.omit(NPP_statistical[,c("lon","lat","CLM_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d10<- aggregate(d10,by=list(d10$lon,d10$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t10 <- stepwise_lm(d10,"CLM_NPP")
t10[[2]]
mod10<- (lm(CLM_NPP~Tg_a+PPFD_a+vpd_a,data=d10))
summary(mod10)

d11 <- na.omit(NPP_statistical[,c("lon","lat","JSBACH_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d11<- aggregate(d11,by=list(d11$lon,d11$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t11 <- stepwise_lm(d11,"JSBACH_NPP")
t11[[2]]
mod11<- (lm(JSBACH_NPP~Tg_a+PPFD_a+vpd_a,data=d11))
summary(mod11)

d12 <- na.omit(NPP_statistical[,c("lon","lat","LPX_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d12<- aggregate(d12,by=list(d12$lon,d12$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
t12 <- stepwise_lm(d12,"LPX_NPP")
t12[[2]]
mod12<- (lm(LPX_NPP~Tg_a+PPFD_a+vpd_a,data=d12))
summary(mod12)

@@

## Plot partial dependencies
```{r}

@@

## TRENDY analysis - N uptake
```{r}

@@

## TRENDY analysis - NNUE
```{r}

@@

#plot_grid(final1,final2,final3,legend_info,
#          final1b,final1c,final1d,white,
#          final1_nue6,final1_nue8,final1_nue4,white,
#          nrow=3,label_x = 0.8, label_y = 0.8)+white

#ggsave(paste("~/data/output/newphy_fig5.jpg",sep=""), width = 20, height = 15)

#nue and nuptake relation
#also, our simulations
NPP_grassland_remove <- NPP_grassland
forest_NUE <- NPP_forest[,c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                            "CNrt_a","LMA_a","vcmax25_a")]
grassland_NUE <- NPP_grassland_remove[,c("lon","lat","grassland_pred_nuptake","grassland_pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                                         "CNrt_a","LMA_a","vcmax25_a")]
names(grassland_NUE) <- c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                          "CNrt_a","LMA_a","vcmax25_a")
nue_allplots <- as.data.frame(rbind(forest_NUE,grassland_NUE))
nue_allplots$nue <-nue_allplots$pred_npp/nue_allplots$pred_nuptake

@@

#plot_grid(final1_nue1,final1_nue2,final1_nue3,final1_nue4,
#          final1_nue5,final1_nue6,final1_nue7,final1_nue8,
#          nrow=2,label_x = 0.8, label_y = 0.8)+white

#ggsave(paste("~/data/output/newphy_add1.jpg",sep=""), width = 20, height = 10)

@@

## Nuptake or NUE vs. all predictors
```{r}
# n uptake
mod_nue3 <- (lm(pred_nuptake~LMA_a+fAPAR_a+age_a+vpd_a+CNrt_a+Tg_a+vcmax25_a+PPFD_a,data=nue_allplots))
summary(mod_nue3)
nue1c <- visreg(mod_nue3,"LMA_a",type="contrast")
nue2c <- visreg(mod_nue3,"fAPAR_a",type="contrast")
nue3c <- visreg(mod_nue3,"age_a",type="contrast")
nue4c <- visreg(mod_nue3,"vpd_a",type="contrast")
nue5c <- visreg(mod_nue3,"CNrt_a",type="contrast")
nue6c <- visreg(mod_nue3,"Tg_a",type="contrast")
nue7c <- visreg(mod_nue3,"vcmax25_a",type="contrast")
nue8c <- visreg(mod_nue3,"PPFD_a",type="contrast")

final1_nue1 <- ggplot() +geom_line(data = nue1c$fit, aes(LMA_a, visregFit),size=2) +ylab("N uptake") +  xlab("ln LMA") +theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue2 <- ggplot() +geom_line(data = nue2c$fit, aes(fAPAR_a, visregFit),size=2) + xlab("fAPAR") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue3 <- ggplot() +geom_line(data = nue3c$fit, aes(age_a, visregFit),size=2) + xlab("ln age") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue4 <- ggplot() +geom_line(data = nue4c$fit, aes(vpd_a, visregFit),size=2) + xlab("ln D") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue5 <- ggplot() +geom_line(data = nue5c$fit, aes(CNrt_a, visregFit),size=2)+ylab("N uptake")  + xlab("ln soil C/N") +theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue6 <- ggplot() +geom_line(data = nue6c$fit, aes(Tg_a, visregFit),size=2) + xlab("Tg") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue7 <- ggplot() +geom_line(data = nue7c$fit, aes(vcmax25_a, visregFit),size=2) + xlab("ln vcmax25") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue8 <- ggplot() +geom_line(data = nue8c$fit, aes(PPFD_a, visregFit),size=2) + xlab("ln PPFD") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")

#plot_grid(final1_nue1,final1_nue2,final1_nue3,final1_nue4,
#          final1_nue5,final1_nue6,final1_nue7,final1_nue8,
#          nrow=2,label_x = 0.8, label_y = 0.8)+white

#ggsave(paste("~/data/output/newphy_add2.jpg",sep=""), width = 20, height = 10)

```{r}
#validation - BP
NPP_statistical$Measured_BP <- NPP_statistical$TNPP_1

@@

#plot_grid(pp2,pp4,pp5,pp6,pp7,pp8,pp9,pp10,pp11,pp12,pp13,pp14,pp15,
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)','(m)'),
#          nrow=5,label_x = 0.9,label_y=0.92,label_size = 20)+white

#ggsave(paste("~/data/output/newphy_figs5.jpg",sep=""), width = 23, height = 25)

@@

## N uptake validation between models
```{r}
#validation - N uptake
Nmin_statistical$pred_nuptake

>>>>

# Setup 
```{r setup, include=FALSE}
rm(list=ls())
library(MLmetrics)
library(vhs)
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
#remotes::install_github("cj-holmes/vhs")
#devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/") # using beni's latest package.
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

### BP grassland
```{r, warning=FALSE}
#check tnpp grassland
#not filtering any management/non-management! while previous do so
#removing tiandi's grassland
NPP_grassland <- subset(NPP_all,pft=="Grassland" & is.na(Nmin)==TRUE)
grassland_sitemean <- aggregate(NPP_grassland,by=list(NPP_grassland$site), FUN=mean, na.rm=TRUE)

@@

b1 <- as.ggplot(~barplot(vif_bp, main = "VIF of Forest BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b2 <- as.ggplot(~barplot(vif_anpp_tnpp, main = "VIF of Forest ANPP/BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b3 <- as.ggplot(~barplot(vif_anpp_leafnpp, main = "VIF of Forest leaf-NPP/ANPP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b4 <- as.ggplot(~barplot(vif_bp_grass, main = "VIF of Grassland BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "ln PPFD", "ln vpd", "ln soil C/N", "fAPAR")))
plot_grid(b1,b2,b3,b4,
          labels = c('(a)','(b)','(c)','(d)'),
          ncol=2,label_x = 0.9,label_y=0.92)+white
ggsave(paste("./output/newphy_figs6.jpg",sep=""),width = 10, height = 13)
```

@@

```{r}
#fig.2 validation
plot_grid(p1,p2,p5,
          p8,p9,p10,
          p3,p4,p11,
          p6,p12,p7, 
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
ggsave(paste("./output/newphy_fig1.jpg",sep=""),width = 24, height = 25)

@@

plot_grid(a3,a4,a5,a6,a7,a8,
          a9,a10,a11,a12,a13,a14,
          nrow=2,
          rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
          labels = c('(a)',' ','(b)',' ','(c)',' ',
                     '(d)',' ','(e)',' ','(f)',' '))

#this is for showing points
ggsave(paste("./output/newphy_figs5.jpg",sep=""),width = 20, height = 10*(2/3))
```

@@

plot_grid(a3,a4,a5,a6,a7,a8,
          a9,a10,a11,a12,a13,a14,
          nrow=2,
          rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
          labels = c('(a)',' ','(b)',' ','(c)',' ',
                     '(d)',' ','(e)',' ','(f)',' '))
ggsave(paste("./output/newphy_fig2.jpg",sep=""),width = 20, height = 10*(2/3))
```

@@

plot_grid(a1,a2,a3,a4,a5,a6,a7,a8,a9,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/newphy_fig3.jpg",sep=""),width = 22, height = 10)

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/newphy_figs7.jpg",sep=""),width = 22, height = 10)
```

@@

plot_grid(d1,d2,d3,d4,d5,d6,
          d7,d8,d9,d10,d11,d12,
          d13,d14,d15,d16,
          nrow=3,rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
          labels = c('(a)',' ','(b)',' ','(c)',' ',
                     '(d)',' ','(e)',' ','(f)',' ',
                     '(g)',' ','(h)',' '),label_size = 15)+ white

ggsave(paste("./output/newphy_figS2.jpg",sep=""),width = 20, height = 10)

@@

## TRENDY analysis- BP
```{r, warning=FALSE}

@@

Fit models with environmental factors
```{r, warning=FALSE}

@@

#not fitting model basing on stepwise, just directly include all
d1 <- na.omit(NPP_statistical[,c("lon","lat","CABLE_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d1<- aggregate(d1,by=list(d1$lon,d1$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

#mod1 <- (lm(CABLE_NPP~fAPAR_a+Tg_a+vpd_a,data=d1))
mod1 <- (lm(CABLE_NPP~Tg_a+PPFD_a+vpd_a,data=d1))
summary(mod1)

d2 <- na.omit(NPP_statistical[,c("lon","lat","ISAM_npp","Tg_a","PPFD_a","vpd_a","site_a")])
d2<- aggregate(d2,by=list(d2$lon,d2$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod2 <- (lm(ISAM_npp~Tg_a+PPFD_a+vpd_a,data=d2))
summary(mod2)

d3 <- na.omit(NPP_statistical[,c("lon","lat","ISBA_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d3<- aggregate(d3,by=list(d3$lon,d3$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod3 <- (lm(ISBA_NPP~Tg_a+PPFD_a+vpd_a,data=d3))
summary(mod3)

d4 <- na.omit(NPP_statistical[,c("lon","lat","JULES_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d4<- aggregate(d4,by=list(d4$lon,d4$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod4 <- (lm(JULES_NPP~Tg_a+PPFD_a+vpd_a,data=d4))
summary(mod4)

d5 <- na.omit(NPP_statistical[,c("lon","lat","LPJ_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d5<- aggregate(d5,by=list(d5$lon,d5$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod5<- (lm(LPJ_NPP~Tg_a+PPFD_a+vpd_a,data=d5))
summary(mod5)

d6 <- na.omit(NPP_statistical[,c("lon","lat","ORCHIDEE_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d6<- aggregate(d6,by=list(d6$lon,d6$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod6<- (lm(ORCHIDEE_NPP~Tg_a+PPFD_a+vpd_a,data=d6))
summary(mod6)

d7 <- na.omit(NPP_statistical[,c("lon","lat","ORCHICNP_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d7<- aggregate(d7,by=list(d7$lon,d7$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod7 <- (lm(ORCHICNP_NPP~Tg_a+PPFD_a+vpd_a,data=d7))
summary(mod7)

d8 <- na.omit(NPP_statistical[,c("lon","lat","SDGVM_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d8<- aggregate(d8,by=list(d8$lon,d8$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod8<- (lm(SDGVM_NPP~Tg_a+PPFD_a+vpd_a,data=d8))
summary(mod8)

d9 <- na.omit(NPP_statistical[,c("lon","lat","CLASS_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d9<- aggregate(d9,by=list(d9$lon,d9$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod9<- (lm(CLASS_NPP~Tg_a+PPFD_a+vpd_a,data=d9))
summary(mod9)

d10 <- na.omit(NPP_statistical[,c("lon","lat","CLM_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d10<- aggregate(d10,by=list(d10$lon,d10$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod10<- (lm(CLM_NPP~Tg_a+PPFD_a+vpd_a,data=d10))
summary(mod10)

d11 <- na.omit(NPP_statistical[,c("lon","lat","JSBACH_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d11<- aggregate(d11,by=list(d11$lon,d11$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

mod11<- (lm(JSBACH_NPP~Tg_a+PPFD_a+vpd_a,data=d11))
summary(mod11)

d12 <- na.omit(NPP_statistical[,c("lon","lat","LPX_NPP","Tg_a","PPFD_a","vpd_a","site_a")])
d12<- aggregate(d12,by=list(d12$lon,d12$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))
mod12<- (lm(LPX_NPP~Tg_a+PPFD_a+vpd_a,data=d12))
summary(mod12)

@@

## Plot partial dependencies
```{r, warning=FALSE}

@@

## TRENDY analysis - N uptake
```{r, warning=FALSE}

@@

## TRENDY analysis - NUE
```{r, warning=FALSE}

@@

plot_grid(final1,final2,final3,legend_info,
          final1b,final1c,final1d,white,
          final1_nue6,final1_nue8,final1_nue4,white,
          nrow=3,label_x = 0.8, label_y = 0.8)+white

ggsave(paste("./output/newphy_fig4.jpg",sep=""), width = 20, height = 15)

## Nuptake or NUE vs. all predictors
```{r, warning=FALSE}
#nue and nuptake relation
#also, our simulations
NPP_grassland_remove <- NPP_grassland
forest_NUE <- NPP_forest[,c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                            "CNrt_a","LMA_a","vcmax25_a")]
grassland_NUE <- NPP_grassland_remove[,c("lon","lat","grassland_pred_nuptake","grassland_pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                                         "CNrt_a","LMA_a","vcmax25_a")]
names(grassland_NUE) <- c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                          "CNrt_a","LMA_a","vcmax25_a")
nue_allplots <- as.data.frame(rbind(forest_NUE,grassland_NUE))
nue_allplots$nue <-nue_allplots$pred_npp/nue_allplots$pred_nuptake

@@

plot_grid(final1_nue1,final1_nue2,final1_nue3,final1_nue4,
          final1_nue5,final1_nue6,final1_nue7,final1_nue8,
          nrow=2,label_x = 0.8, label_y = 0.8)+white

ggsave(paste("./output/newphy_figs8.jpg",sep=""), width = 20, height = 10)

@@

```{r, warning=FALSE}
#validation - BP
NPP_statistical$Measured_BP <- NPP_statistical$TNPP_1

@@

plot_grid(pp2,pp4,pp5,pp6,pp7,pp8,pp9,pp10,pp11,pp12,pp13,pp14,pp15,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)','(m)'),
          nrow=5,label_x = 0.9,label_y=0.92,label_size = 20)+white

ggsave(paste("./output/newphy_fortable2.jpg",sep=""), width = 23, height = 25)

@@

## N uptake validation between models
```{r, warning=FALSE}
#validation - N uptake
Nmin_statistical$pred_nuptake
